Differentially Private Bayesian Inference

### 2018-04-13 main.tex
update

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

\subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

@@

@@

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
\subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

@@

\subsubsection{Security Analysis}
We will then prove that exponential mechanism with local sensitivity is non-differentialy private.
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} 
& = exp\left(
\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} - 
\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
\right)  \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
\right) \\
& = \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}.
\end{split}
\end{equation*}

Without loss of generality, we consider the case that $\Delta_{l}u(y) < \Delta_{l}u(x)$, $r = arg(\max\limits_{r' \in R}\{u(x,r')\}) = arg(\min\limits_{r' \in R}\{u(y,r')\})$ and $\Delta_{l}u(y) = u(x,r) - u(y,r)$. We have:
\begin{equation*}
\begin{split}
\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
& > \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(x,r) + u(y,r'))}{2 \Delta_{l}u(x)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(y,r) + u(x,r'))}{2 \Delta_{l}u(y)})}\\
& > \frac
{|R|\ exp(\frac{\epsilon (u(x,r) + u(y,r))}{2 \Delta_{l}u(x)})}
{|R|\ exp(\frac{\epsilon (u(y,r) + u(x,r))}{2 \Delta_{l}u(y)})}\\
& = exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)})).
\end{split}
\end{equation*}

From Eq. \ref{equ_utility}, $\{u(x,r') \leq 0|r' \in R\}$ and $\{u(y,r') \leq 0|r' \in R\}$, we can infer that $r = arg(\max\limits_{r \in R}\{u(x,r')\}) = \bysinfer(x)$ and $u(x,r) = 0$.From $\Delta_{l}u(y) = u(x,r) - u(y,r)$, we can also infer that $\Delta_{l}u(y) = - u(y,r)$. Then, the following relationship between $u(x,r)$, $u(y,r)$, $\Delta_{l}u(x)$ and $\Delta_{l}u(y)$:
\begin{equation*}
\begin{split}
- \Delta_{l}u(x) & < \Delta_{l}u(y) \\
\Delta_{l}u(x) - \Delta_{l}u(y) & < 2 \Delta_{l}u(x) \\
- \Delta_{l}u(y) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
u(y,r) (\Delta_{l}u(y) - \Delta_{l}u(x)) 
& < 2 \Delta_{l}u(x) \Delta_{l}u(y) \\
\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} & > 2.
\end{split}
\end{equation*}

% \begin{equation*}
% \begin{split}
% \frac{\Delta_{l}u(x)}{\Delta_{l}u(y)} & > 0\\
% & > \frac{\Delta_{l}u(x)}{2u(y,r)}\\
% & = \frac{\Delta_{l}u(x) + 0}{2u(y,r)} \\
% & = \frac{\Delta_{l}u(x) + 2 u(x,r)}{2u(y,r)}
% \end{split}
% \end{equation*}
holds.

Then we can have:
\begin{equation*}
\begin{split}
& exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)}))\\
& > exp(\frac{\epsilon}{2} * 2) \\
& = exp(\epsilon),
\end{split}
\end{equation*}
i.e.
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
& > exp(\epsilon).
\end{split}
\end{equation*}

Since there are cases where exponential mechanism with local sensitivity's privacy loss is greater than $e^{\epsilon}$. we can say it is non-differentially private.
% \begin{equation*}
% \begin{split}
% & \epsilon = 0.1\\
% data size = 2\\
% the prior is Beta(2，2)\\
% data set x = [1,0,]\\
% data set y = [0,0]\\
% -0.313380201461\\
% -0.0\\
% -0.313380201461\\
% 3 3\\
% 0.313380201461\\
% 0.322043464396\\
% 0.355913071207\\
% 0.322043464396\\
% -0.0\\
% -0.313380201461\\
% -0.57735026919\\
% 2 4\\
% 0.375460728684\\
% 0.360050126956\\
% 0.331218326999\\
% 0.308731546045
% \end{split}
% \end{equation*}

% Without loss of generality, we consider the case that $\Delta_{l}u(y) > \Delta_{l}u(x)$ and $\Delta_{l}u(x) = u(x,r) - u(y,r)$. We have:
% \begin{equation*}
% \begin{split}
% exp\left(
% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
% \right)
% & > exp\left(
% \frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)}
% - \frac{\epsilon u(y,r)}{2 \Delta_{l}u(x)}
% \right)\\
% & = exp\left(
% \frac{\epsilon u(x,r) - \epsilon u(y,r)}{2 \Delta_{l}u(x)}
% \right) \\
% & = exp(\frac{\epsilon}{2});
% \end{split}
% \end{equation*}

% \textcolor{red}{For the second part:
% , we have:
% \begin{equation*}
% \begin{split}
% \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(x)} 
% & < \frac{\epsilon u(y,r')}{2 \Delta_{l}(y)} - \frac{\epsilon u(x,r')}{2 \Delta_{l}(y)}\\
% & \leq \frac{\epsilon}{2}
% \end{split}
% \end{equation*}
% I cannot replace $exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}(y)})$ in $\left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)$ with $ > exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}(x)})$.
% So, I cannot find the relationship between the whole part and $exp(\epsilon)$.}

% For the second part:
% \begin{equation*}
% \begin{split}
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)
% & < \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < exp(\frac{\epsilon}{2})
% \end{split}
% \end{equation*}

% For the second part(a tighter bound):
% \begin{equation*}
% \begin{split}
% & \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right) \\
% & = \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(x)})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \cdot
% \sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
% \right)\\
% & < \left(\frac
% {exp(\frac{\epsilon}{2})}
% {exp(\frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})}
% \right)\\
% & < exp(\frac{\epsilon}{2} - \frac{\Delta _{l}(y) - \Delta _{l}(x)}{\Delta _{l}(x)  \Delta _{l}(y)})
% \end{split}
% \end{equation*}

\subsection{Exponential Mechanism of Varying Sensitivity}
\label{subsec_emvs}
\subsubsection{Mechanism Setting up}

\subsubsection{Security Analysis}

\subsection{Exponential Mechanism of Smooth Sensitivity}
\label{subsec_emss}
\subsubsection{Mechanism Setting up}

\subsubsection{Security Analysis}

\section{Privacy Fix}

\subsection{Propositions}
Assume we have a prior distribution $beta(1,1)$, an observed data set $x \in \{0,1\}^n$, $n>0$. We use the $x+1$ and $x-1$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if\ BayesInfer}(x) = beta(a_1 + 1,b_1 + 1)\\
&\mathsf{then}\mathsf{\ BayesInfer}(x + 1) = beta((a_1 + 1) +1, (b_1 - 1)+1)\\
&\quad \quad \mathsf{\ BayesInfer}(x - 1) = beta((a_1 - 1) +1, (b_1 + 1)+1),\\
\end{split}
\end{equation*}
\end{small}

$x_0$ to denote:
\begin{small}
\begin{equation*}
\begin{split}
&\mathsf{if}\ n\ is\ even\\
&\mathsf{then}\ \bysinfer(x_0) = beta(\frac{n}{2} + 1, \frac{n}{2} + 1)\\
&\mathsf{else}\ \bysinfer(x_0) = \{beta(\frac{n+1}{2} + 1, \frac{n-1}{2} + 1),\\
&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad beta(\frac{n - 1}{2} + 1, \frac{n + 1}{2} + 1)\}
\end{split}
\end{equation*}
\end{small}

$\betafun(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.

Then, we have the following three statements, and proofs of the statements.
\renewcommand{\labelenumi}{\Roman{enumi}}
\begin{enumerate}
\item $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$;

or $\hlg (\bysinfer(x), \bysinfer(x + 1)) > \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\forall x \leq x_0$.

\item $\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x + 1)),\forall x \geq x_0$;

$\Delta_{l}u(x) = \hlg (\bysinfer(x),\bysinfer(x - 1)),\forall x \leq x_0$.

\item $\forall x \neq x_0: \Delta_{l}u(x) > \Delta_{l}u(x_0)$.
\end{enumerate}

\subsection{proof}

\subsubsection{Statement I}
We use the MI (Mathematical Induction) method to prove the first statement.

\begin{proof}
Since the Hellinger distance is symmetric, if we prove the $\hlg (\bysinfer(x), \bysinfer(x + 1)) < \hlg (\bysinfer(x + 1), \bysinfer(x + 2))\ \forall x \geq x_0$, the other part when $\forall x \leq x_0$ also holds.

1. if $x = x_0$, $\hlg (\bysinfer(x_0), \bysinfer(x_0 + 1)) < \hlg (\bysinfer(x_0 + 1), \bysinfer(x_0 + 2))$ holds:

% \twocolumn{
\begin{small}
\begin{equation*}
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
\end{equation*}
\end{small}

Since $n > 0$, it always holds.

2. if $x = x_0 + m$ holds, then also $x = x_0 + m + 1$ holds:

i.e $\hlg(beta(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m), beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1)) 
< \hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2))$
is what we know:

\begin{small}
\begin{equation*}
\begin{split}
\sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}
& < \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
\frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

Now, we need to proof $\hlg(beta(\frac{n}{2} + 1 + m + 1, \frac{n}{2} + 1 - m - 1), beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2)) 
< \hlg(beta(\frac{n}{2} + 1 + m + 2, \frac{n}{2} + 1 - m - 2), beta(\frac{n}{2} + 1 + m + 3, \frac{n}{2} + 1 - m - 3))$ by using what we know.

From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:

\begin{small}
\begin{equation*}
\begin{split}
 \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
\frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
\sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
\hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{small}

i.e. $ x = x_0 + m + 1$ also holds when $x = x_0 + m$ is valid.
\end{proof}

\subsubsection{Statement II}
\begin{proof}

\begin{equation*}
\begin{split}
\because \footnote{the symbol of $\because$ here means because}
\quad 		& \Delta_l u(x) = \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}} |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r) \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \footnote{the symbol of $\therefore$ here means therefore}
\quad 	& \Delta_l u(x) = \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}} \hlg(\bysinfer(x), \bysinfer(y')),\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)), \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1)) < \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))  > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1)) = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}

From above, we can conclude the Statement II.

\subsubsection{Statement III}
\begin{proof}
From Statement I and Statement II, we can conclude that:
\begin{equation*}
\begin{split}
\mathsf{when} \quad	& x > x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x + 1) > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
\mathsf{when} \quad	& x < x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x - 1)  > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
\end{split}
\end{equation*}

i.e $\forall \ x \neq x_0, \Delta_l u(x) > \Delta_l u(x_0)$.

\section{Smooth sensitivity}
\label{sec_smoo}

>>>>

\section{Bayesian Inference Based on Beta-Bernoulli Distribution}
\label{sec_bayesInfer}

\section{Algorithm Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

% \subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

@@

The basic exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

@@

% \subsubsection{Security Analysis}
% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
% \begin{equation*}
% \begin{split}
% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
% & =\frac
% {\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
% {\frac
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
% & = \left(\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp\left(\frac
% {\epsilon (u(x,r) - u(y,r))}
% {2 \Delta_{g}u}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & \leq
% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp(\epsilon).
% \end{split}
% \end{equation*}

% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

@@

The exponential mechanism with local sensitivity is non differential privacy\cite{dwork2014algorithmic}.

\subsection{Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

\subsubsection{Algorithm Setting Up}
The candidate set and utility function are still the same as before, differ only in the sensitivity. It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:

\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
\end{equation*}
where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the sliding property holds:

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}
